Exponential distribution Simulation 
========================================================

This is the first part of the project for the Statistical inference course.
The exponential distribution was simulated with the function rexp(n,lambda), using lambda = 0.2

### 0. The simulation
First run thousand times the simulated data for n=40, lambda=0.2 and stored the mean of each sample in a vector

```{r,echo=TRUE}

    lambda = 0.2
    n= 40
    times = 1000
    
     vectMeans<- NULL
     vectVar<-NULL
     vectStDev<-NULL

    samples <- replicate(times,rexp(n,lambda))

    for (i in 1:times)
      {
         vectMeans <- c(vectMeans,mean(samples[,i])
         vectVar <- c(vectVar,var(samples[,i]))
         vectStDev<-c(vectStDev, sd(samples[,i]))
      }
     
     
#     vectAllData<-NULL
#     
#     for (i in 1:1000){
#      expoData <- rexp(n,lambda)
#      vectMeans <- c(vectMeans,mean(expoData))
#      vectVar <- c(vectVar,var(expoData))
#      vectStDev<-c(vectStDev, sd(expoData))
#      vectAllData <- c(vectAllData,expoData)
# }
    
```

### 1. Where the distribution is centered at and compare it to the theoretical center of the distribution

```{r, echo=TRUE}
     theMean<-mean(vectMeans)
     theDensity <- density(vectMeans)
     plot(theDensity)
```
The mean of the simulated data was `r theMean` , which is very close to the theoretical center of the distribution: 1/0.2=5

### 2.  How variable it is and compare it to the theoretical variance of the distribution
The theoretical variance for the exponential distribution is 1/(lambda*lambda), in this case: 1/(0.2 * 0.2)=25

```{r, echo=TRUE}
  
     variance<- mean(vectVar)
   
```
The variance for the simulated data is `r variance`,  again very close to the theoretical value.
### 3. Show that the distribution is approximaterly normal
```{r, echo=TRUE}
  #hist(expoData)
```
### 4.  Evaluate the coverage of the confidence interval

```{r, echo=TRUE}
# http://www4.stat.ncsu.edu/~boos/slab/slabe/lab7.html
#        lowL <- theMean - 1.96 * mean(vectStDev)/sqrt(n)
#        uppL <- theMean - 1.96 * mean(vectStDev)/sqrt(n)
#        incorrectLow<- length(vectMeans[vectMeans < lowL])
#        incorrectUpp<- length(vectMeans[uppL < vectMeans])
#        total<- (incorrectUpp + incorrectLow)/1000
#        total
#        incorrectLow
#        incorrectUpp
hist(samples)
```