Exponential distribution Simulation 
========================================================

This is the first part of the project for the Statistical inference course.
The exponential distribution was simulated with the function rexp(n,lambda), using lambda = 0.2

### 0. The simulation
First run thousand times the simulated data for n=40, lambda=0.2 and stored the mean of each sample in a vector

```{r,echo=TRUE}

    lambda = 0.2
    n= 40
    times = 1000
    
     vectMeans<- NULL
     vectVar<-NULL
     vectStDev<-NULL

    samples <- replicate(times,rexp(n,lambda))

    for (i in 1:times)
      {
         vectMeans <- c(vectMeans,mean(samples[,i]))
         vectVar <- c(vectVar,var(samples[,i]))
         vectStDev<-c(vectStDev, sd(samples[,i]))
      }
    
```

### 1. Where the distribution is centered at and compare it to the theoretical center of the distribution

```{r, echo=TRUE}
     theMean<-mean(vectMeans)
     theDensity <- density(vectMeans)
     plot(theDensity)
     abline(v=theMean,col='blue')
```

The mean of the simulated data was `r theMean` , which is very close to the theoretical center of the distribution: 1/0.2=5

### 2.  How variable it is and compare it to the theoretical variance of the distribution
The theoretical variance for the exponential distribution is 1/(lambda*lambda), in this case: 1/(0.2 * 0.2)=25

```{r, echo=TRUE}
  
     variance<- mean(vectVar)
   
```
The variance for the simulated data is `r variance`,  again very close to the theoretical value.
### 3. Show that the distribution is approximaterly normal
The next graph is a qqplot that evaluates the fit of the sample data with a normal distribution. It uses the theoretical quantiles of the distribution

```{r, echo=TRUE}
      
     hist(vectMeans)
     
```

As seen in the histogram above, the data seems to follow a  normal distribution.


### 4.  Evaluate the coverage of the confidence interval
Calculates the confidence interval for each sample, then count how many times the population mean it is not in the intervals

```{r, echo=TRUE}
   
    
   lower <- array(0,times)
   upper <- array(0,times)
   
   
   for (k in 1:times)
   {
         
        lower[k] <- vectMeans[k] - (1.96 * vectStDev[k]/sqrt(n))
        upper[k] <- vectMeans[k] + (1.96 * vectStDev[k]/sqrt(n))
        
     }

   noLower <- length(which(theMean < lower))
   noUpper <- length(which(upper < theMean))
   badCases <- (noLower+noUpper)/times

```
The coverage of the confidence interval is close to 95%, the population mean it is not in the interval in near `r badCases` , that is near 5%